Toward an Aspect-oriented Cache Autoloading Framework with Annotation

### 2019-02-16 paper.tex
modified at  Feb 16, 2019 - refactor   - section 3.1.2(Inplementation)  ... done   - section 3.1.3(Load Waiting Strategy) ... done   - section 3.1.4(Auto Loading Strategy) ... partly done - math block changed to italic, $anything$ -> \textit{anything}

\begin{abstract}
In recent years, researches focus on addressing the query bottleneck issue using data cache in the Internet-of-Things. However, the challenges of this method are how to implement autonomous management of data cache. In this paper, we propose an aspect-oriented cache autoloading framework (ACALFA). The architecture, annotation, expression are introduced to address cache auto load. There are some features for improving performance, such as load waiting, autoloading, loose coupling, and batch delete of cache. The result of experiments indicated that our approach is nearly 25\% faster than other cache frameworks in the scenario that data size is enormous and concurrency is very high.
\end{abstract}

@@

\subsection{Contributions}
In this paper, we propose an aspect-oriented cache auto load framework with annotation (ACALFA for short). Contributions of our cache framework are concluded as follows.

\begin{itemize}
  \item Avoid cache breakdown and cache penetration using load waiting and autoloading. Autoloading can implement hot-spot data pre-loading. The cache work because the data can be obtained from memory and cut down the read back of source. To further reduce the read back of source, we can make the hot-spot data lurk in memory constantly and update it regularly. Moreover, the data that need to a long time to process also benefit from this strategy, system can load them before peak coming. Load waiting can reduce the server pressure when load data from database. Once the cache miss, there are many requests flowing into the database, but for the same data. Load wait strategy select a leader to request the data, others wait until the data are provided by the leader.
  \item Loose coupling of business and cache logic using AOP. The purpose of AOP is proposed to decrease the costs of cache maintenance.
  \item Batch delete of cache. It is inevitable that it leads the inconsistency of physical database and cache data. It is difficult to restore the key of the related cache by programs if the query statement is involved. Therefore, the precise batch delete of cache is proposed using hash tables. When this cache need to be removed, the system will remove the record of corresponding hash table directly.
\end{itemize}

\subsection{Organization}
The remainder of the paper is organized as follows. The current work of cache framework is discussed in Section \ref{RelatedWork}. In Section \ref{Framework}, aspect-oriented cache autoloading framework with annotation (ACALFA) is proposed. Architecture, annotation, expression of the aspect-oriented cache auto load framework are introduced. In Section \ref{Experiments}, the response time, cache improvement and pressure experiments show that our framework are effective and efficient. Brief conclusions and future research directions are outlined in the last section.

@@

\section{Aspect-oriented Cache Auto Load Framework with Annotation}
\label{Framework}

@@

\begin{figure} [htb]
\centering
\includegraphics[width=1.0\linewidth]{img/architecture}
\caption{\label{architecture}Architecture of aspect-oriented cache auto load framework with annotation (ACALFA).}
\end{figure}

Figure \ref{architecture} gives the architecture of our proposed aspect-oriented cache auto load framework with annotation (ACALFA). ACALFA reads data from in-memory database when it hits the cache, while reads data from relational database management system (RDBMS) when it misses the cache. ACALFA writes data to both in-memory cache and RDBMS. They synchronize the data with each other. This framework is used to reduce the load of reading/writing service of big data applications. Load waiting and auto loading strategy is achieved by decreasing the concurrency number of read back of source RDBMS.

\begin{figure} [htb]
\centering
\includegraphics[width=1.0\linewidth]{img/process}
\caption{\label{process}Data processing of aspect-oriented cache auto load framework with annotation (ACALFA).}
\end{figure}

Figure \ref{process} shows the data processing of aspect-oriented cache auto load framework with annotation (ACALFA). Using aspect-oriented thinking, cache framework is loosely coupled with business and cache logic. Cache interceptor is used to intercept before/after the execution of business method, then generate the cache key by annotation to trigger cache query. Cache entry is triggered by custom cache events and its corresponding handler. Annotation, a form of metadata, provides data about a program that is not part of the program itself. Cache annotation is used to describe the point cut (cache logic) of our cache framework. It includes cache key, expire time, and cache type. The data of the in-memory cache is loaded by a unique cache key. Cache key is created by the expression in annotation dynamically.

@@

\subsubsection{Implementation}
There are several components to implement ACALFA:

\begin{itemize}
    \item $CacheInterceptor$: It is used to intercept the business logic to add cache logic in the pointcut. The cache key is delivered to by the annotation.
    \item $CachePointCut$: It is is a set of join points. It allows where exactly to apply advice, this allows separation of concerns and helps in modularizing business logic.
    \item $CacheHandler$: It is charged with process control rather than specific business. It parses cache configurations - are loaded from $@Cache$ Annotation - by expression parser. The crucial cache configurations are as follow:
    \begin{itemize}
        \item $CacheKey$ is a cache identification expression, which can generate cache key dynamically according to the parameters.
        \item $ExpireTime$ is a value to set up the cache expire time, the default value is 120(s).
        \item $IsCacheable$ is a expression that return true or false to determined whether the cache can be cachable.
        \item $IsAutoload$ is a expression that return true or false to determined whether the cache should be auto loading.
    \end{itemize}
    \item $AutoLoadHandler$: It is seen as auto load executor maintaining multiple internal tasks and queues. The cache that is going to expire update by loading asynchronous. The details will be described in following sections.
    \item $DataHelper$: It works with Data Access Object (DAO) for fetching data from database and prevents the excessive traffic from coming into database. Therefore, the load waiting strategy is implemented in this component.
    \item $CacheHelper$: It encapsulates functions of operating cache, such as $get$ and $set$.
\end{itemize}

@@

Load waiting strategy is used to prevent multiple requests for requesting same data from the physical database at the same time. It is a kind of avoiding of resource wasting. Once hot-spot data miss and there are mass of requests flowing into database within a very short period time. The principle is to elect a leader to fetch data from database, others, requesting for data with the same key, will be suspended until the leader processed. Figure \ref{loadwaiting} shows the process of load waiting strategy.

The framework identify the same requests by the cacheKey, which is a unique identification for the data. Processing is a hash map storing the different processing requests. A request want to fetch the data from database, $DataHelper$ will search whether the same request is being processed. The framework try to get request from Processing hash map by cacheKey. If the result is null, it indicates that the request is a new request. In the concurrency, there are mass of the requests, the framework will select the first request as a leader to fetch data from physical data, others are waiting until the leader notify them and bring the data back. The specific load waiting strategy algorithm is as Algorithm \ref{loadwaitingalg}.

\begin{algorithm}
\caption{Load waiting strategy algorithm \textit{loadwaiting}}
\label{loadwaitingalg}
\begin{algorithmic}[1]
\REQUIRE ~~\\
  String $cacheKey$;\\
  Map $hashMap$;
\ENSURE ~~\\

@@

\subsubsection{Auto Loading Strategy}
Generally, each cache have its own expired time, which it's not suitable for high-frequent cache or time-consuming data in in-memory cache. Once expired, the system has to fetch those data from data source, which may consume lots of resources and make response slow. Therefore, those types of data should reside in the memory until they don't take too many resources when fetching them.

Figure \ref{autoloading} shows the management of the query autoloading queue. $hashTable$, which providing a method called $putIfAbsent$ to avoid duplicate tasks and controlling the number of auto load tasks, is a storage for auto load assignments. $taskQueue$ is taken from $hashTable$ by a unified strategy, like LRU. In distributed scenario, the standardized sequence of tasks help the system reduce the read back of source, because others can fetch data from cache rather than database after first server loaded. Auto load, however, is a double-edged, the system may become unstable if the amount of auto load tasks were too much or update frequency were too high. Accordingly, a strict inspection should be applied. We assume that $t_n$(ms) is current time, $t_{fr}$(ms) is the first request time, $t_{lr}$(ms) is last request time,  $t_a$(ms) is the average of fetching time, $c$ is the times of cache usage, $t_{to}$ is a preset parameter determining cache time out. There are three main aspects as follow:

\begin{itemize}
    \item Remove if the targeting cache is not requested for a long time. The time of not be requested is get from $t_{nr} = t_n - t_{lr}$, if $t_{nr} > t_{to}$, the task will be discarded.
    \item Remove if efficiency of fetching data from database is high. This may be confused. The intention of auto load is pre-load the data that cost a lot of time and resources and be accessed frequently. Hence, the data that obtaining efficiency is high should not occupy the space of auto load. The standard of determination is $c > 100$ and $t_a < 10$.
    \item Remove if usage rate is low. If the cache, which is requested only once within the preset timeout, were added to auto load queue, that will go against the purposes of auto load. Therefore, only removing the task that the targeting cache is not requested for a long time is not enough. The usage rate can be get from $r = \frac{c}{t_u}, t_u = {{t_n - t_{fr}}\over{3600000}}$, the meaning of $r$ is how much the cache is requested per hours. If the task has been running for more than 1 hour and the average loading time is less than 1000 ms and $r$ is less than 60, the task will be removed.
\end{itemize}{}

The last part of auto load is when to refresh the cache. As a pre-loading schema, the cache should be refreshed before expired. For this reason, setting alarm time is valuable. Experiments prove that the default alarm time should be set $t_e - 120$ if $t_e \geq 600$ or $t_e - 60$ if $t_e < 600$, which $t_e$ is a preset parameter determining cache expired time.

@@

\subsection{Annotation}
Aspects at particular join points enable the modularization of concerns such as cache management that cut across multiple types and objects. We use interceptor as an advice in aspects. Cache pointcuts are put in all DAO classes to implement business hierarchy. Several annotations are designed to describe pointcuts. This framework need intercept the methods with cache annotation and apply cache strategy. There are several annotations, such as $@Cache$, $@ExCache$, $@CacheDeleteKey$, $@CacheDeleteTransactional$, and $@LocalCache$.

\subsubsection{Cache}
$@Cache$ that describes the entrance of in-memory caches is one of the most critical annotations. This cache framework will parse the cache configuration in $@Cache$ after intercepting this annotation, such as expiration time, the expression of the cache key. When the function of DAO returns data (the data is obtained from the physical database), the framework synchronize the data into the in-memory cache.

\subsubsection{ExCache}
$@ExCache$ implements generating multiple caches in one request. It is used to reduce the number of read back of source as long as sorting out the relationship between the cache. The implement of this feature is that framework will determine whether $@Cache$ contains $@ExCache$ items or not. If yes, framework will generate a new cache according to the configuration.

\subsubsection{CacheDelete}
$@CacheDelete$ and $@CacheDeleteKey$ implement the cache deleting strategy. $@CacheDelete$ is used to remove the cache. $@CacheDeleteKey$ is used to generate the cache key that will be removed. The structures are shown as Table \ref{CacheDelete} and \ref{CacheDeleteKey}.

\begin{table}[htb]
\begin{center}
 \caption{\label{CacheDelete}$CacheDelete$ annotation.}
 \begin{tabular}{lll}
 \toprule
Name & Type & Description\\
 \midrule
value & CacheDeleteKey[] & CacheDeleteKey array\\
\bottomrule
 \end{tabular}
\end{center}
\end{table}

\begin{table*}[htb]
\begin{center}
 \caption{\label{CacheDeleteKey}$CacheDeleteKey$ annotation.}
 \begin{tabular}{lll}
 \toprule
Name & Type & Description\\
 \midrule
condition & String & Condition expression and it will return true or false.\\ %The caches are deleted only when its return is true\\
value & String[] & An array saving the cache key expression\\
hfield & String & Expression of hash table field\\
\bottomrule
 \end{tabular}
\end{center}
\end{table*}

@@

\begin{itemize}
  \item $addFunction$ means adding a custom method. In the class of expression parser, there is a hash table which is named $customFunction$s. The key of $customFunctions$ is EL expression, and the value of that is a custom method. In this way, the relationship between expression and custom method is created.
  \item $getExpressionValue$. Converting an expression to an expected value. The parameters are shown in Table \ref{getExpressionValue}. This function traverses the keys in $customFunctions$ to register those custom functions.
\end{itemize}

@@

\subsection{Experiment Setup}
Three experiments are designed to illustrate the ACALFA performance in high-concurrency scenario. The metrics are response time, resource consumption and stability. Response time is for validating the optimization of auto load, especially for time-consuming tasks and high-frequent business. Resource consumption is for validating the load wait performance when handling the same requests. Stability testing uses multiple threads to access applications simultaneously to simulate high concurrency. The server with ACALFA is an Intel Core i7 @ 3.40GHz CPU, 16GB memory, and 100Mbps bandwidth, and this server runs a 64-bit Windows 10 with a Java 1.8 64-bit server JVM. Another server with MySQL database runs on Ali ECS Cloud Server: 2 core 2.60GHz Intel Xeon E5-2650 CPU machines with 4 GB RAM, 40GB SSD and 100 Mbps Ethernet. The system is CentOS 6.8 x64. Spring Cache, a well-known cache management framework at j2ee, will be compared with ACALFA for performance. The dataset, the structure is shown in Table \ref{VTS}, is selected 4,000 records randomly from a voting system.

@@

We set up six experiments to test the ACALFA effect. Cache expired time we set was 120s and enabled auto load and load wait for ACALFA. Exp1, exp3 and exp5 used ACALFA, on the contrary, others used Spring Cache. The experiment sets are as follow:

\begin{itemize}
    \item Exp1 \& Exp2: The resources that will be requested were not in cache. Therefore, the frameworks should fetch data from database.
    \item Exp3 \& Exp4: The response time when cache hit.
    \item Exp5 \& Exp6: After exp1 and exp2 120s, in other words, cache expired, we send requests again for validating the effect of auto load.
\end{itemize}

@@

We use the 90th percentile response time for performance measurement. Figure \ref{exp1-2} and figure \ref{exp3-4} shows the response time is increasing with the increase of number of threads. The performance of two cache management systems when cache miss or cache hit is same roughly. Figure \ref{exp5-6}, however, shows vast difference between ACALFA with auto load and Spring Cache. The reason is obviously: ACALFA will reload data when the cache is going to expire, but Spring Cache can't. According to this range of experiments, we found auto load is suited to the hot-spot data and has better cache effects for the more time-consuming or more frequent data.

@@

The purpose of a cache is to duplicate frequently accessed or important data in such a way that it can be accessed very fast and close to where it is needed. In the big data era, caching generally moves data from a low cost. This paper introduces an aspect-oriented cache auto load framework with annotation. Several experiments are illustrated that our cache framework has a good effect on the complex business with high concurrency. In the future work, memory resource cost will be optimized to increase cache hit ratio.

>>>>

\begin{abstract}
In recent years, researches focus on addressing the query bottleneck issue using data cache in the Internet-of-Things. However, the challenges of this method are how to implement autonomous management of data cache. In this paper, we propose an aspect-oriented cache autoloading framework (ACALFA). The architecture, annotation, expression are introduced to address cache auto loading. There are some features for improving performance, such as load waiting, autoloading, loose coupling, and batch delete of cache. The result of experiments indicated that our approach is nearly 25\% faster than other cache frameworks in the scenario that data size is enormous and concurrency is very high.
\end{abstract}

@@

\subsection{Contributions}
In this paper, we propose an aspect-oriented cache auto loading framework with annotation (ACALFA for short). Contributions of our cache framework are concluded as follows.

\begin{itemize}
  \item Avoid cache breakdown and cache penetration using load waiting and autoloading. Autoloading can implement hot-spot data pre-loading. The cache work because the data can be obtained from memory and cut down the read back of source. To further reduce the read back of source, we can make the hot-spot data lurk in memory constantly and update it regularly. Moreover, the data that need to a long time to process also benefit from this strategy, system can load them before peak coming. Load waiting can reduce the server pressure when load data from database. Once the cache miss, there are many requests flowing into the database, but for the same data. Load waiting strategy select a leader to request the data, others wait until the data are provided by the leader.
  \item Loose coupling of business and cache logic using AOP. The purpose of AOP is proposed to decrease the costs of cache maintenance.
  \item Batch delete of cache. It is inevitable that it leads the inconsistency of physical database and cache data. It is difficult to restore the key of the related cache by programs if the query statement is involved. Therefore, the precise batch delete of cache is proposed using hash tables. When this cache need to be removed, the system will remove the record of corresponding hash table directly.
\end{itemize}

\subsection{Organization}
The remainder of the paper is organized as follows. The current work of cache framework is discussed in Section \ref{RelatedWork}. In Section \ref{Framework}, aspect-oriented cache autoloading framework with annotation (ACALFA) is proposed. Architecture, annotation, expression of the aspect-oriented cache auto loading framework are introduced. In Section \ref{Experiments}, the response time, cache improvement and pressure experiments show that our framework are effective and efficient. Brief conclusions and future research directions are outlined in the last section.

@@

\section{Aspect-oriented Cache Auto Loading Framework with Annotation}
\label{Framework}

@@

\begin{figure} [htb]
\centering
\includegraphics[width=1.0\linewidth]{img/architecture}
\caption{\label{architecture}Architecture of aspect-oriented cache auto loading framework with annotation (ACALFA).}
\end{figure}

Figure \ref{architecture} gives the architecture of our proposed aspect-oriented cache auto loading framework with annotation (ACALFA). ACALFA reads data from in-memory database when it hits the cache, while reads data from relational database management system (RDBMS) when it misses the cache. ACALFA writes data to both in-memory cache and RDBMS. They synchronize the data with each other. This framework is used to reduce the load of reading/writing service of big data applications. Load waiting and auto loading strategy is achieved by decreasing the concurrency number of read back of source RDBMS.

\begin{figure} [htb]
\centering
\includegraphics[width=1.0\linewidth]{img/process}
\caption{\label{process}Data processing of aspect-oriented cache auto loading framework with annotation (ACALFA).}
\end{figure}

Figure \ref{process} shows the data processing of aspect-oriented cache auto loading framework with annotation (ACALFA). Using aspect-oriented thinking, cache framework is loosely coupled with business and cache logic. Cache interceptor is used to intercept before/after the execution of business method, then generate the cache key by annotation to trigger cache query. Cache entry is triggered by custom cache events and its corresponding handler. Annotation, a form of metadata, provides data about a program that is not part of the program itself. Cache annotation is used to describe the point cut (cache logic) of our cache framework. It includes cache key, expire time, and cache type. The data of the in-memory cache is loaded by a unique cache key. Cache key is created by the expression in annotation dynamically.

@@

\subsubsection{Implementation}

ACALFA consists of many components to reduce servers pressure. \textit{Cache interceptor} stores all the cache logic and intercepts all the objects with \textit{@Cache} annotation to implement features, like auto loading, load waiting, etc. The configurations are delivered by the \textit{@Cache} annotation. \textit{Cache pointcut} is a set of join points. It allows where exactly to apply advice, this allows separation of concerns and helps in modularizing business logic. \textit{Cache handler} helps ACALFA determine what is next step, instead implements the specific tasks. It parses cache configurations from \textit{@Cache} annotation by the expression parser. The primary cache configurations are listed below:

\begin{itemize}
    \item \textit{Cache key} defines an unique name to identify them by a expression that could generate a string dynamically according to the parameters.
    \item \textit{Expire time} informs ACALFA of the time that the cache should be removed. The value would be 120(s) if not specify.
    \item \textit{Is cacheable} is a expression that returns a Boolean value. If false, ACALFA will not cache them even though they has \textit{@Cache} annotation.
    \item \textit{Is autoload} is a expression that returns a Boolean value too. The cache cannot reside in the memory if false.
\end{itemize}

\textit{Autoload handler} is the actual cache executor in ACALFA, including multiple internal tasks and queues. The cache that is about to expire and should be auto loaded is updated by it asynchronously. The details about how to implement them will be described in the following part. \textit{Data helper} works with Data Access Object(DAO) that obtains data from database directly. To prevent excessive traffic from flowing into database server, ACALFA resolves it by implementing a strategy, called load wait, in \textit{Data helper}. \textit{Cache handler} encapsulates the functions to operate cache, for example, \textit{get} and \textit{set} in Redis.

@@

Load waiting strategy is used to prevent multiple requests for requesting same data from the physical database at the same time. It is a kind of avoiding of resource wasting. There are mass of traffic flows into database server within a short time once hot-spot data missed. Load waiting selects a leader to get data from database by \textit{Data helper}, instead allows all requests to access to database. Others will be suspended until the leader returns the data. The method to determine which is the same request is by the \textit{Cache key} field that is set in the \textit{@Cache} annotation. Figure \ref{loadwaiting} shows the process of load waiting strategy.

The load waiting strategy algorithm is shown in Algorithm \ref{loadwaitingalg}. \textit{Processing} is a hash map that stores processing requests with different \textit{cache key}. The framework try to get request object from \textit{Processing} hash map by \textit{cache key}. Generally speaking, ACALFA considers this is a new type of request and selects a first arrived request as the leader if returns null. On the contrary, others are waiting until the leader inform them that it is ready for returning values for them.

\begin{algorithm}
\caption{Load waiting strategy algorithm \textit{loadwaiting}}
\label{loadwaitingalg}
\begin{algorithmic}[1]
\REQUIRE ~~\\
  String cacheKey;\\
  Map hashMap;
\ENSURE ~~\\

@@

\subsubsection{Auto Loading Strategy}
In general, developer should preset an expired time for every type of cache. However, the time limit is not suitable for the hot-spot or time-consuming data, especially when traffic peak comes. The cache management system has to load the data from database once cache missed, which may cause response slow, even the server inaccessible. Therefore, to resolve it ACALFA applies a method, called auto loading, that allows those type of data to reside in the memory until they are no longer accessed frequently.

Figure \ref{autoloading} shows the management of the query autoloading queue. \textit{hashTable}, which providing a method called \textit{putIfAbsent} to avoid duplicate tasks and controlling the number of auto loading tasks, is a storage for auto loading assignments. \textit{taskQueue} is taken from \textit{hashTable} by a unified strategy, like LRU. In distributed scenario, the standardized sequence of tasks help the system reduce the read back of source, because others can fetch data from cache rather than database after first server loaded. Auto loading, however, is a double-edged, the system may become unstable if the amount of auto loading tasks were too much or update frequency were too high. Accordingly, a strict inspection should be applied. We assume that $t_n$(ms) is current time, $t_{fr}$(ms) is the first request time, $t_{lr}$(ms) is last request time,  $t_a$(ms) is the average of fetching time, $c$ is the times of cache usage, $t_{to}$ is a preset parameter determining cache time out. There are three main aspects as follow:

\begin{itemize}
    \item Remove if the targeting cache is not requested for a long time. The time of not be requested is get from $t_{nr} = t_n - t_{lr}$, if $t_{nr} > t_{to}$, the task will be discarded.
    \item Remove if efficiency of fetching data from database is high. This may be confused. The intention of auto loading is pre-load the data that cost a lot of time and resources and be accessed frequently. Hence, the data that obtaining efficiency is high should not occupy the space of auto loading. The standard of determination is $c > 100$ and $t_a < 10$.
    \item Remove if usage rate is low. If the cache, which is requested only once within the preset timeout, were added to auto loading queue, that will go against the purposes of auto loading. Therefore, only removing the task that the targeting cache is not requested for a long time is not enough. The usage rate can be get from $r = \frac{c}{t_u}, t_u = {{t_n - t_{fr}}\over{3600000}}$, the meaning of $r$ is how much the cache is requested per hours. If the task has been running for more than 1 hour and the average loading time is less than 1000 ms and $r$ is less than 60, the task will be removed.
\end{itemize}{}

The last part of auto loading is when to refresh the cache. As a pre-loading schema, the cache should be refreshed before expired. For this reason, setting alarm time is valuable. Experiments prove that the default alarm time should be set $t_e - 120$ if $t_e \geq 600$ or $t_e - 60$ if $t_e < 600$, which $t_e$ is a preset parameter determining cache expired time.

@@

\subsection{Annotation}
Aspects at particular join points enable the modularization of concerns such as cache management that cut across multiple types and objects. We use interceptor as an advice in aspects. Cache pointcuts are put in all DAO classes to implement business hierarchy. Several annotations are designed to describe pointcuts. This framework need intercept the methods with cache annotation and apply cache strategy. There are several annotations, such as \textit{@Cache}, \textit{@ExCache}, \textit{@CacheDeleteKey}, \textit{@CacheDeleteTransactional}, and \textit{@LocalCache}.

\subsubsection{Cache}
\textit{@Cache} that describes the entrance of in-memory caches is one of the most critical annotations. This cache framework will parse the cache configuration in \textit{@Cache} after intercepting this annotation, such as expiration time, the expression of the cache key. When the function of DAO returns data (the data is obtained from the physical database), the framework synchronize the data into the in-memory cache.

\subsubsection{ExCache}
\textit{@ExCache} implements generating multiple caches in one request. It is used to reduce the number of read back of source as long as sorting out the relationship between the cache. The implement of this feature is that framework will determine whether \textit{@Cache} contains \textit{@ExCache} items or not. If yes, framework will generate a new cache according to the configuration.

\subsubsection{CacheDelete}
\textit{@CacheDelete} and \textit{@CacheDeleteKey} implement the cache deleting strategy. \textit{@CacheDelete} is used to remove the cache. \textit{@CacheDeleteKey} is used to generate the cache key that will be removed. The structures are shown as Table \ref{CacheDelete} and \ref{CacheDeleteKey}.

\begin{table}[htb]
\begin{center}
 \caption{\label{CacheDelete}\textit{@CacheDelete} annotation.}
 \begin{tabular}{lll}
 \toprule
Name & Type & Description\\
 \midrule
value & CacheDeleteKey[] & CacheDeleteKey array\\
\bottomrule
 \end{tabular}
\end{center}
\end{table}

\begin{table*}[htb]
\begin{center}
 \caption{\label{CacheDeleteKey}\textit{@CacheDeleteKey} annotation.}
 \begin{tabular}{lll}
 \toprule
Name & Type & Description\\
 \midrule
condition & String & Condition expression and it will return true or false.\\ %The caches are deleted only when its return is true\\
value & String[] & An array saving the cache key expression\\
hfield & String & Expression of hash table field\\
\bottomrule
 \end{tabular}
\end{center}
\end{table*}

@@

\begin{itemize}
  \item \textit{Add function} means adding a custom method. In the class of expression parser, there is a hash table which is named \textit{custom functions}. The key of \textit{custom functions} is EL expression, and the value of that is a custom method. In this way, the relationship between expression and custom method is created.
  \item \textit{Get expression value}. Converting an expression to an expected value. The parameters are shown in Table \ref{getExpressionValue}. This function traverses the keys in \textit{custom functions} to register those custom functions.
\end{itemize}

@@

\subsection{Experiment Setup}
Three experiments are designed to illustrate the ACALFA performance in high-concurrency scenario. The metrics are response time, resource consumption and stability. Response time is for validating the optimization of auto loading, especially for time-consuming tasks and high-frequent business. Resource consumption is for validating the load waiting performance when handling the same requests. Stability testing uses multiple threads to access applications simultaneously to simulate high concurrency. The server with ACALFA is an Intel Core i7 @ 3.40GHz CPU, 16GB memory, and 100Mbps bandwidth, and this server runs a 64-bit Windows 10 with a Java 1.8 64-bit server JVM. Another server with MySQL database runs on Ali ECS Cloud Server: 2 core 2.60GHz Intel Xeon E5-2650 CPU machines with 4 GB RAM, 40GB SSD and 100 Mbps Ethernet. The system is CentOS 6.8 x64. Spring Cache, a well-known cache management framework at j2ee, will be compared with ACALFA for performance. The dataset, the structure is shown in Table \ref{VTS}, is selected 4,000 records randomly from a voting system.

@@

We set up six experiments to test the ACALFA effect. Cache expired time we set was 120s and enabled auto loading and load waiting for ACALFA. Exp1, exp3 and exp5 used ACALFA, on the contrary, others used Spring Cache. The experiment sets are as follow:

\begin{itemize}
    \item Exp1 \& Exp2: The resources that will be requested were not in cache. Therefore, the frameworks should fetch data from database.
    \item Exp3 \& Exp4: The response time when cache hit.
    \item Exp5 \& Exp6: After exp1 and exp2 120s, in other words, cache expired, we send requests again for validating the effect of auto loading.
\end{itemize}

@@

We use the 90th percentile response time for performance measurement. Figure \ref{exp1-2} and figure \ref{exp3-4} shows the response time is increasing with the increase of number of threads. The performance of two cache management systems when cache miss or cache hit is same roughly. Figure \ref{exp5-6}, however, shows vast difference between ACALFA with auto loading and Spring Cache. The reason is obviously: ACALFA will reload data when the cache is going to expire, but Spring Cache can't. According to this range of experiments, we found auto loading is suited to the hot-spot data and has better cache effects for the more time-consuming or more frequent data.

@@

The purpose of a cache is to duplicate frequently accessed or important data in such a way that it can be accessed very fast and close to where it is needed. In the big data era, caching generally moves data from a low cost. This paper introduces an aspect-oriented cache auto loading framework with annotation. Several experiments are illustrated that our cache framework has a good effect on the complex business with high concurrency. In the future work, memory resource cost will be optimized to increase cache hit ratio.
